---
title: Test Shiny in Rmarkdown
output: html_notebook
runtime: shiny
---

[RMarkdown in Shiny Application](https://stackoverflow.com/questions/33499651/rmarkdown-in-shiny-application)

[runtime: shiny` not compatible with bookdown cross-references #1063](https://github.com/rstudio/rmarkdown/issues/1063)

TODO Why only `ggplotly` isn't required to be wrapped in `render***` ?

```{r, echo = FALSE}
suppressMessages({ suppressWarnings({
  library(shiny)
  library(ggplot2)
  library(plotly)
  library(theme)
  library(shinyr)
  library(data.table)
})})
```

```{r}
shiny::renderTable(head(mtcars))
```

```{r}
# theme_switcher <- function (id = "theme_switcher") {
#     # callModule(id = id, function(input, output, session) {
#         observeEvent(input$theme, {
#             output$theme_out <- renderUI({
#                 theme::theme_switcher_shiny(theme = input$theme)
#             })
#         })
#         theme_switcher_val <<- eventReactive(input$theme, input$theme)
#     # })
# }
```

```{r, echo = FALSE}
# theme_switcher_rmd <- function() {
#   {theme_switcher_in() ; theme_switcher_out() ; theme_switcher()}
# }
# theme_switcher_rmd()
theme_switcher_in() ; theme_switcher_out() ; theme_switcher()

selectInput('n_trace', 'Num of trace',
            c(1, 2, 4, 6, 7, 10), selected = 4)
renderPlotly({
  dt <- data.table(txhousing)[city %in% unique(city)[1:input$n_trace]]
  plot_ly(dt, x = ~date, y = ~median, color = ~city) %>%
    add_lines() %>% rangeslider() %>% layout(title = 'abc')
})
```

Note that the output format of the R Markdown document must be an HTML format. That is, the *document* should generate a web page (a *.html file). Non-HTML formats such as *pdf_document* and word_document will not work with the Shiny runtime. Please also note that some presentation formats are also *HTML* formats, such as `ioslides_presentation` and slidy_presentation.

```{r}
1+1
```

```{r}
reactable::reactable(iris)
```

```{r}
p <- ggplot(mpg, aes(displ, hwy, color = class)) + geom_point()
renderPlot(p)
```

```{r}
ggplotly()
```
